Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-18 article/draft.tex
add reference

Aside from the disappearance of data due to content moderation, some essential metrics for the study of misinformation are not accessible via main APIs. 
In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API (REF). 
Hence, researchers can only build proxies for this metric based on available data (see section \ref{reduce_fb} for an example). 
Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs, with the exception of the {\it withheld}  and {\it possibly sensitive content} interstitials in the Twitter API v2. 
For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube. 
Again, this disrupts the monitoring of the platforms' interventions and the assessment of their impact (Pasquetto, Swire-Thompson, Amazeen et al. (2020)~\cite{pasquetto}).

@@

A last concern regards the increasing restrictions to access APIs \cite{api}.
In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs
\footnote{https://about.fb.com/news/2018/04/restricting-data-access/}, 
and CrowdTangle is today a reliable source for researchers to access Facebook data. 
But CrowdTangle has recently been used by journalists to shown that Facebook is spreading biased information
\footnote{\url{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}, \url{https://twitter.com/facebookstop10}. 
The last link is a Twitter account showing each day the ten most shared link on Facebook, most of them coming from extreme right and misinformation sources. 
Facebook has reacted to this here: \url{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}}
, and a general suspicion is growing that journalists' researchers' access to the API might be shut down in a near future.
\footnote{\url{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}, \url{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}}
Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs, although in our personal experience we never managed to get access to the Twitter API when we described our intend to use the Twitter developer platform as `academic'.
\footnote{The token was given only when we described a `hobbyist' intent.}
It should also be noted that the number of Tweets you can retrieve has decreased between the Twitter API V1 and V2. 
In the V2, there is a monthly cap of 10,000,000 Tweets for academic research projects
\footnote{https://developer.twitter.com/en/docs/projects/overview},
while there was no monthly limit in the V1, only a limit in the number of requests that could be made in a 15-minute window
\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
We thus noticed that we could get around 10 times more Tweets per month with the V1 than the V2 for one specific collection.

>>>>

Aside from the disappearance of data due to content moderation, some essential metrics for the study of misinformation are not accessible via main APIs. 
In particular, the $reach$ of posts on Facebook, which is the number of people who actually see a given post, cannot be recovered from the CrowdTangle API.
\footnote{\url{https://help.crowdtangle.com/en/articles/4558716-understanding-and-citing-crowdtangle-data}} 
Hence, researchers can only build proxies for this metric based on available data (see section \ref{reduce_fb} for an example). 
Furthermore, to the best of our knowledge, fields related to flags, notices and information panels are not available on the official APIs, with the exception of the {\it withheld}  and {\it possibly sensitive content} interstitials in the Twitter API v2. 
For the purposes of the present research we thus had to scrape this information from Facebook, Twitter and YouTube. 
Again, this disrupts the monitoring of the platforms' interventions and the assessment of their impact (Pasquetto, Swire-Thompson, Amazeen et al. (2020)~\cite{pasquetto}).

@@

A last concern regards the increasing restrictions to access APIs \cite{api}.
In April 2018, likely as a response to the Cambridge Analytica scandal, Facebook severely limited access to their official APIs
\footnote{\url{https://about.fb.com/news/2018/04/restricting-data-access/}, \url{http://thepoliticsofsystems.net/2018/08/facebooks-app-review-and-how-independent-research-just-got-a-lot-harder/}}, 
and CrowdTangle is today a reliable source for researchers to access Facebook data. 
But CrowdTangle has recently been used by journalists to shown that Facebook is spreading biased information
\footnote{\url{https://www.economist.com/graphic-detail/2020/09/10/facebook-offers-a-distorted-view-of-american-news}, \url{https://twitter.com/facebookstop10}. 
The last link is a Twitter account showing each day the ten most shared link on Facebook, most of them coming from extreme right and misinformation sources. 
Facebook has reacted to this here: \url{https://about.fb.com/news/2020/11/what-do-people-actually-see-on-facebook-in-the-us/}}
, and a general suspicion is growing that journalists' researchers' access to the API might be shut down in a near future.
\footnote{\url{https://www.nytimes.com/2021/07/14/technology/facebook-data.html}, \url{https://www.bloomberg.com/news/articles/2021-08-03/facebook-disables-accounts-tied-to-nyu-research-project}}
Regarding Twitter and YouTube, it is still possible and relatively easy to access their official APIs, although in our personal experience we never managed to get access to the Twitter API when we described our intend to use the Twitter developer platform as `academic'.
\footnote{The token was given only when we described a `hobbyist' intent.}
It should also be noted that the number of Tweets you can retrieve has decreased between the Twitter API V1 and V2. 
In the V2, there is a monthly cap of 10,000,000 Tweets for academic research projects
\footnote{https://developer.twitter.com/en/docs/projects/overview},
while there was no monthly limit in the V1, only a limit in the number of requests that could be made in a 15-minute window
\footnote{https://developer.twitter.com/en/docs/twitter-api/v1/rate-limits}.
We thus noticed that we could get around 10 times more Tweets per month with the V1 than the V2 for one specific collection.
